Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach

### 2021-02-15 2_revisions/V5_ITT_minor_revision/0_manuscript_blind/itt-emotion_blind.tex
Added V5 in revisions and latexdiff of newer version

    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service. \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry. It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer. As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction. Previous studies on the dimensions of culture that influence differences in expectations have also been performed in the past \cite{donthu1998cultural}. Western and Chinese customers can then have very different satisfaction and dissatisfaction factors since they have different backgrounds and cultures. These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have. These expectations will be there from the moment that they choose the hotel throughout their stay. In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.

@@

  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip}, as well as the travel site \textit{TripAdvisor}. We then determined the most commonly used words that contribute to positive and negative opinions in a review. We did this using Shannon's entropy to extract keywords from their vocabulary. These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers. We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC). We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews. We split the dataset in price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels. We observed the frequency of the terms in the dataset to extract the most utilized words in either kind of review. We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}. Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel. Soft attributes are non-physical aspects of the hotel, those that regard service, staff behavior, or hotel management, which are able to be changed by the staff or management. Hard attributes are related to physical and environmental aspects, such as facilities,  infrastructure, the surroundings of the hotel, which are impossible to change directly by the staff alone.

@@

    However, we needed to make the data and comparisons we draw from each of these datasets fair. For that purpose, we filtered both databases only to contain reviews from hotels in both datasets, using their English names to do a search match. We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges. In addition, we selected only the hotels that had pricing information available. We extracted the lowest price possible for a room or bed for one night, and the highest price possible for one night as well. The difference in pricing can be from better room settings, such as double or twin rooms, or suites of several classes depending on the hotel. Regardless of the reason, the highest-priced room can be an indicator of the hotel's class indirectly, which can give us an insight into the kind of service that is offered. After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{557}. The overlapping date range for reviews was from July 2014 to July 2017. Within these hotels, from \textit{Ctrip} there was \num[group-separator={,}]{48070} reviews comprised of \num[group-separator={,}]{101963} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41137} reviews comprised of \num[group-separator={,}]{348039} sentences. After filtering the data, we found that the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general.

    The price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night, to high-end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve. Customers' expectations can vary greatly depending on the pricing of the hotel room they stay at. Therefore, we made observations on the distribution of pricing in our database's hotels and binned the data by price ranges, decided by consideration of the objective of stay. We show these distributions in Figure \ref{fig:price_dist}. The structure of the data after division by price is shown in Table \ref{tab:exp_notes}. This table also includes the results of emotional classification after applying our SVC, as explained in \ref{sentimentanalysis}. The first three price ranges (0 to 2500 yen, 2500 to 5000 yen, 5000 to 10,000 yen) would correspond to low-class hotels or even hostels on the lower end, and cheap business hotels on the higher end. Further on, there are business hotels in the next range (10,000 to 15,000 yen). After that, the stays could be at Japanese style \textit{ryokan} when traveling in groups, high-class business hotels, luxury love hotels, or higher class hotels (15,000 to 20,000 yen, 20,000 to 30,000 yen). Further than that is more likely to be \textit{ryokan} or high class resorts or five-star hotels (30,000 to 50,000 yen, 50,000 to 100,000 yen, 100,000 to 200,000 yen). Note that because of choosing the highest price per one night in each hotel, the cheapest two price ranges (0 to 2500 yen, 2500 to 5000 yen) are empty, despite some rooms being priced at 2000 yen per night. Because of this, other tables will omit these two price ranges.

@@

    A dependency parser analyzes the grammatical structure of a sentence, detecting connections between words and describing the action and direction of those connections. We show an example of these dependencies in Figure \ref{fig:depparse}. In this study, we use the Stanford NLP Dependency Parser, as described by \cite{chen-EMNLP:2014}. A list of dependencies used by this parser is detailed by \cite{marneffe_manning_2016_depparse_manual}. In more recent versions, they use an updated dependency tag list from Universal Dependencies \cite[][]{zeman2018conll}. In our study, this step was necessary to extract adjective modifiers and their subject. We did that by parsing the entire database and extracting instances of a few determined dependency codes. One of these dependency codes is ``amod'', which stands for ``adjectival modifier''. This is used when an adjective modifies a noun directly (e.g., A big apple). The other dependency code we used was ``nsubj'', or nominal subject, which is the class's syntactic subject. We used this one for cases where the adjective is modifying the noun indirectly through other words (e.g., The apple is big). This dependency does not necessarily only include a combination of adjectives and nouns. However, it can also be connected with copular verbs, nouns, or other adjectives. We saw it necessary also to perform a Part of Speech (POS) tagging of these clauses.

@@

    In this study, we were interested in identifying combinations of adjectives, some verbs, and nouns. We also needed to filter away bad combinations that were brought by the versatility of nominal subject dependencies. For this purpose, we identified the tags for nouns, verbs, and adjectives in Chinese and English, with the English tags being a bit more varied. What would be called adjectives in English corresponds more to stative verbs in Chinese, so we needed to extract those as well. We show a detailed description of the chosen tags in Table \ref{tab:target_postag}. We also show a detailed description of the tags we needed to filter. We selected these tags heuristically by observing commonly found undesired pairs, in Table \ref{tab:filter_postag}.

@@

    The sentiment analysis was performed using the methodology described by \cite{Aleman2018ICAROB}. Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite[][]{powers2011}. The selected SVM keywords would then clearly represent the user driving factors leading to positive and negative emotions. We also performed experiments to choose the best value of the parameter C used in the SVM. C is a constant that affects the optimization process when minimizing the error of the separating hyperplane. Low values of C give some freedom of error, which minimizes false positives. However, depending on the data, it can increase false negatives. Inversely, high C values will likely result in minimal false negatives, but a possibility of false positives. SVM performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}. Examples of tagged sentences are shown in Table \ref{tab:training_examples}.

@@

    Shannon's entropy can be used to observe the probability distribution of each word inside the corpus. A word that is included in many documents will have a high entropy value for that set of documents. Opposite to this, a word appearing in only one document will have an entropy value of zero.

@@

    Our study used the SVM classification process's linear kernel, defined by the formula (\ref{eq:svm1}) below. Each training sentence is a point of data, a row in the vector \(x\). Each column represents a feature; in our case, the quantities of each of the keywords in that particular sentence. The labels of previously known classifications (1 for positive, 0 for negative) for each sentence comprise the \(f(x)\) vector. The Weight Vector \(w\) is comprised of the influences each point has had in the training process to define the hyperplane angle. The bias coefficient \(b\) determines its position.

    During the SVM learning algorithm, each data point classified incorrectly causes a change in the weight vector to classify new data correctly. These changes to the weight vector are greater for features close to the separating hyperplane. These features have stronger changes because they needed to be taken into account to classify with a minimal error. Sequentially, the weight vector can be interpreted as a numerical representation of each feature's effect on each class's classification process. Below we show the formula for the weight vector \(w\) (\ref{eq:svm_weight}), where \(x\) is the training data and each vectorized sentence \(x_i\) in the data is labeled \(y_i\). Each cycle of the algorithm alters the value of \(w\) by \(\alpha\) to reduce the number of wrong classifications. This equation shows the last value of \(\alpha\) after the end of the cycle.

@@

    We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative for our training data. The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25. We applied this SVC to classify the rest of our data collection. Subsequently, the positive and negative sentences counts shown in Table \ref{tab:exp_notes} are the result of applying our SVC for classification.

@@

    Some keywords in these lists are adjectives, such as the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' mentioned before. In order to understand those, we performed the dependency parsing, and part of speech tagging explained in section \ref{textprocessing}. While there were many of these connections, we only considered the top 4 used keyword connections per adjective per price range. We show the most used Chinese adjectives in positive keywords in Table \ref{tab:adj_zh_pos}, and for negative Chinese adjective keywords in Table \ref{tab:adj_zh_neg}. Similarly, for English adjectives used in positive sentences we show the most common examples in Table \ref{tab:adj_en_pos}, and for adjectives used in negative sentences in Table \ref{tab:adj_en_neg}.

@@

    To further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel. We define hard attributes as matters regarding physical or environmental aspects of the hotel, such as facilities, location, or infrastructure, that would be impractical for the hotel to change, such as the hotel's surroundings and location, or impractical and expensive to change, such as matters requiring construction costs, which are possible but regarding investment in infrastructure. On the other hand, soft attributes are the non-physical attributes of the hotel service and staff behavior that are practical to change through management. For example, the hotel's services or the cleanliness of the rooms are soft attributes. For our purposes, amenities, clean or good quality bedsheets or curtains, and other physical attributes that are part of the service and not of the physical structure of the hotel are also considered soft attributes. Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.

@@

    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges. This word is followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''. When we look at the adjectival pairing of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that mostly, they praise either the location, the service, breakfast, or English availability. When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively. With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities. However, both populations consider the hotel's location and transport availability (subways and trains) nearby as secondary but still essential points in their satisfaction with a hotel. The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness and the service of breakfast.

@@

    We also can observe some keywords that are not considered by their counterparts. For example, English-speaking customers mentioned tobacco smell in many reviews, while it was not statistically identified as a problem for their Chinese counterparts. On the other hand, while it appears in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night. Meanwhile, the term ``shopping'' only appears in the 20,000 to 30,000 yen per night top 10 positive keywords list for English-speakers.

    In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds react to hard and soft attributes of the hotel, and how they differ in those reactions. Here we define hard attributes as those relating to physical, structural or environmental aspects of the hotel, which are often impossible or impractical to change directly by the hotel management and staff, such as facilities, infrastructure, the surroundings, view, or location convenience. On the other hand, soft attributes are those that the hotel staff and management could practically change directly, such as improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness. In our study, we find that Chinese tourists are mostly positively reacting more to the hotel's hard attributes. There is a slightly hard leaning (53\%) concern with hard attributes in negative sentences, albeit it is more uniform in this instance. English-speaking tourists, on the other hand, are both positively and negatively more responsive to soft attributes. In the case of negative keywords, English-speaking tourists are overwhelmingly more concerned with the hotel's soft attributes dissatisfaction somehow.

    One factor that both populations have in common is, when perceiving the hotel negatively, ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)'', ``dated'', ``outdated'', or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel are being criticized across, surprisingly, most price ranges. This is, however, a hard attribute, and is unlikely to change for most hotels.

@@

    We found that mainland Chinese tourists are satisfied mostly by a big and clean space provided by the Japanese hotels. From the adjectival pairings that we extracted with dependency parsing and POS tagging in Table \ref{tab:adj_zh_pos}, we can observe that mostly they mean big and clean rooms. Other mentions are also big markets nearby or a big bed. We can observe that across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increases as the hotel increases in price. However, we can see that they still react positively in a significant manner in cheaper hotels. Inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area)'', we can see that there are also many references to the public bathing facilities in the hotel. We can also see them mentioned as a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring)''. In Japan, there is what is called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o})'', which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities. On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})''. They can either be bathing in the natural source of the water or using the hot springs in artificially made bath facilities. It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes. It can be a cultural shock for many tourists, but this is a fundamental attraction for many.

@@

    One key component we found in Chinese customer satisfaction soft factors is the inclusion of breakfast within the hotel. While other food-related words were extracted, most of them were general, like ``food'' or ``eating,'' and in a lower ranking. In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words. The word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' is also observed across all price ranges, although at different priorities in each of them. However, we assert that it is an important factor. Observing word pairs from the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also see that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired as ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top 4 pairings. It is only slightly lower on other categories, although it is not shown on the table. Thus we consider that a recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast to increase good reviews.

@@

    From the satisfaction factors of English-speaking tourists, we can see that at least three words relate directly to staff friendliness and services, being ``staff'', ``helpful'' and ``friendliness'' in the general database. The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges, and only third in one of them. Adding to that, ``helpful'' and ``friendly'' follow it lower in the list in most price ranges. The word ``good'' is mostly about the location, the service, breakfast, or English availability in Table \ref{tab:adj_en_pos}. Like Chinese customers, Western customers also seem to enjoy the included breakfasts when it comes to their satisfaction keyword pairings. However, the word does not appear directly in the top 10 list as in their Chinese counterparts. The words ``helpful'' and ``friendly'' are mostly paired with ``staff'', ``concierge'', ``desk'', and ``service''. When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively.

@@

    While less high in priority, the price range of 15,000 to 20,000 yen hotels also mentions ``free'' as one of the top 10 positive keywords, paired mostly with ``wifi''. This price range is mostly for business hotels where we infer users would be expecting this feature the most. Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.

@@

  Below we explore the possible interactions with Japanese hospitality; what the differences between Chinese and Western tourists were; what is the possible cause for them; how they vary across different price ranges; and what they imply for the industry. We also discuss the differences between the hotel's hard and soft attributes and how they contribute to the satisfaction of customers.

>>>>

    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service. \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry. It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer. As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction. Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past \cite{donthu1998cultural}. Western and Chinese customers can then have very different satisfaction and dissatisfaction factors since they have different backgrounds and cultures. These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have. These expectations will be there from the moment that they choose the hotel throughout their stay. In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.

@@

  We have extracted a large number of text reviews from a Chinese portal site \textit{Ctrip} and the travel site \textit{TripAdvisor}. We then determined the most commonly used words that contribute to positive and negative opinions in a review. We did this using Shannon's entropy to extract keywords from their vocabulary. These positive and negative keywords allow us to perform a Support Vector Machine (SVM) based emotional classification of the reviews in large quantities, saving time and resources for the researchers. We classified the sentences in the extracted reviews as emotionally positive or negative, using an optimized Support Vector Classifier (SVC). We then applied a dependency parsing to the reviews and a Part of Speech tagging (POS tagging) to observe the relationship between adjective keywords and other nouns used in the reviews. We split the dataset into price ranges to observe the satisfaction factors and their differences between lower-class and higher-class hotels. We observed the frequency of the terms in the dataset to extract the most utilized words in either review. We show an overview of this methodology in Figure \ref{fig:method-overview}, which is an updated version of the methodology used by \cite{Aleman2018ICAROB}. Finally, we also observed if the satisfaction factors were soft or hard attributes of the hotel. Soft attributes are non-physical aspects of the hotel, those that regard service, staff behavior, or hotel management, which can be changed by the staff or management. Hard attributes are related to physical and environmental aspects, such as facilities,  infrastructure, and the hotel's surroundings, which are impossible to change by the staff alone.

@@

    However, we needed to make the data and comparisons we draw from each of these datasets fair. For that purpose, we filtered both databases only to contain reviews from hotels in both datasets, using their English names to do a search match. We also filtered them to be in the same date range and cut off reviews outside of each other's date ranges. In addition, we selected only the hotels that had pricing information available. We extracted the lowest price possible for a room or bed for one night, and the highest price possible for one night as well. The difference in pricing can be from better room settings, such as double or twin rooms or suites of several classes, depending on the hotel. Regardless of the reason, the highest-priced room can be an indicator of the hotel's class indirectly, giving us insight into the kind of service offered. After filtering, we found that the number of hotels in common in the data collected was \num[group-separator={,}]{557}. The overlapping date range for reviews was from July 2014 to July 2017. Within these hotels, from \textit{Ctrip} there was \num[group-separator={,}]{48070} reviews comprised of \num[group-separator={,}]{101963} sentences, and from \textit{TripAdvisor} there was \num[group-separator={,}]{41137} reviews comprised of \num[group-separator={,}]{348039} sentences. After filtering the data, we found that the number of reviews was similar for both English and Chinese reviews, but that English reviews tend to be longer in general.

    The price for a night in these hotels ranges from low priced capsule hotels at 2000 yen per night to high-end hotels \num[group-separator={,}]{188000} yen a night as the far ends of the bell curve. Customers' expectations can vary greatly depending on the pricing of the hotel room they stay at. Therefore, we made observations on the distribution of pricing in our database's hotels and binned the data by price ranges, decided by consideration of the objective of stay. We show these distributions in Figure \ref{fig:price_dist}. The structure of the data after division by price is shown in Table \ref{tab:exp_notes}. This table also includes the results of emotional classification after applying our SVC, as explained in \ref{sentimentanalysis}. The first three price ranges (0 to 2500 yen, 2500 to 5000 yen, 5000 to 10,000 yen) would correspond to low-class hotels or even hostels on the lower end and cheap business hotels on the higher end. Further on, there are business hotels in the next range (10,000 to 15,000 yen). After that, the stays could be at Japanese style \textit{ryokan} when traveling in groups, high-class business hotels, luxury love hotels, or higher class hotels (15,000 to 20,000 yen, 20,000 to 30,000 yen). Further than that is more likely to be \textit{ryokan} or high class resorts or five-star hotels (30,000 to 50,000 yen, 50,000 to 100,000 yen, 100,000 to 200,000 yen). Note that because of choosing the highest price per one night in each hotel, the cheapest two price ranges (0 to 2500 yen, 2500 to 5000 yen) are empty, despite some rooms being priced at 2000 yen per night. Because of this, other tables will omit these two price ranges.

@@

    A dependency parser analyzes the grammatical structure, detecting connections between words, and describing the action and direction of those connections. We show an example of these dependencies in Figure \ref{fig:depparse}. This study uses the Stanford NLP Dependency Parser, as described by \cite{chen-EMNLP:2014}. A list of dependencies used by this parser is detailed by \cite{marneffe_manning_2016_depparse_manual}. In more recent versions, they use an updated dependency tag list from Universal Dependencies \cite[][]{zeman2018conll}. In our study, this step was necessary to extract adjective modifiers and their subject. We did that by parsing the entire database and extracting instances of a few determined dependency codes. One of these dependency codes is ``amod'', which stands for ``adjectival modifier''. This is used when an adjective modifies a noun directly (e.g., A big apple). The other dependency code we used was ``nsubj'', or nominal subject, the class's syntactic subject. We used this one for cases where the adjective is modifying the noun indirectly through other words (e.g., The apple is big). This dependency does not necessarily only include a combination of adjectives and nouns. However, it can also be connected with copular verbs, nouns, or other adjectives. We saw it necessary also to perform a Part of Speech (POS) tagging of these clauses.

@@

    In this study, we were interested in identifying combinations of adjectives, some verbs, and nouns. We also needed to filter away bad combinations that were brought by the versatility of nominal subject dependencies. For this purpose, we identified the tags for nouns, verbs, and adjectives in Chinese and English, with the English tags being a bit more varied. What would be called adjectives in English corresponds more to stative verbs in Chinese, so we needed to extract those as well. We show a detailed description of the chosen tags in Table \ref{tab:target_postag}. We also show a detailed description of the tags we needed to filter. We selected these tags heuristically by observing commonly found undesired pairs in Table \ref{tab:filter_postag}.

@@

    The sentiment analysis was performed using the methodology described by \cite{Aleman2018ICAROB}. Keywords are determined by a comparison of Shannon's entropy \cite[][]{shannon1948} between two classes by a factor of \(\alpha\) for one class and \(\alpha'\) for the other, and then they are used in an SVM \cite[][]{cortes1995}, optimizing keywords to select the best performing classifier using the \(F_1\)-measure \cite[][]{powers2011}. The selected SVM keywords would then clearly represent the user driving factors leading to positive and negative emotions. We also performed experiments to choose the best value of the parameter C used in the SVM. C is a constant that affects the optimization process when minimizing the error of the separating hyperplane. Low values of C give some freedom of error, which minimizes false positives. However, depending on the data, it can increase false negatives. Inversely, high C values will likely result in minimal false negatives but a possibility of false positives. SVM performance results are displayed in  Tables \ref{tab:svm_f1_zh} and \ref{tab:svm_f1_en}. Examples of tagged sentences are shown in Table \ref{tab:training_examples}.

@@

    Shannon's entropy can be used to observe the probability distribution of each word inside the corpus. A word included in many documents will have a high entropy value for that set of documents. Opposite to this, a word appearing in only one document will have an entropy value of zero.

@@

    Our study used the SVM classification process's linear kernel, defined by the formula (\ref{eq:svm1}) below. Each training sentence is a data point, a row in the vector \(x\). Each column represents a feature; in our case, the quantities of each of the keywords in that particular sentence. The labels of previously known classifications (1 for positive, 0 for negative) for each sentence comprise the \(f(x)\) vector. The Weight Vector \(w\) is comprised of the influences each point has had in the training process to define the hyperplane angle. The bias coefficient \(b\) determines its position.

    During the SVM learning algorithm, each data point classified incorrectly causes a change in the weight vector to correctly classify new data. These changes to the weight vector are greater for features close to the separating hyperplane. These features have stronger changes because they needed to be taken into account to classify with a minimal error. Sequentially, the weight vector can be interpreted as a numerical representation of each feature's effect on each class's classification process. Below we show the formula for the weight vector \(w\) (\ref{eq:svm_weight}), where \(x\) is the training data and each vectorized sentence \(x_i\) in the data is labeled \(y_i\). Each cycle of the algorithm alters the value of \(w\) by \(\alpha\) to reduce the number of wrong classifications. This equation shows the last value of \(\alpha\) after the end of the cycle.

@@

    We tagged 159 Chinese sentences and \num[group-separator={,}]{2357} English sentences as positive or negative for our training data. The entropy comparison factors \(\alpha\) and \(\alpha'\) were tested from 1.25 to 6 in intervals of 0.25. We applied this SVC to classify the rest of our data collection. Subsequently, the positive and negative sentence counts shown in Table \ref{tab:exp_notes} result from applying our SVC for classification.

@@

    Some keywords in these lists are adjectives, such as the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' mentioned before. To understand those, we performed the dependency parsing, and part of speech tagging explained in section \ref{textprocessing}. While many of these connections, we only considered the top 4 used keyword connections per adjective per price range. We show the most used Chinese adjectives in positive keywords in Table \ref{tab:adj_zh_pos}, and for negative Chinese adjective keywords in Table \ref{tab:adj_zh_neg}. Similarly, for English adjectives used in positive sentences we show the most common examples in Table \ref{tab:adj_en_pos}, and for adjectives used in negative sentences in Table \ref{tab:adj_en_neg}.

@@

    To further understand the differences in satisfaction and dissatisfaction in Chinese and Western customers of Japanese hotels, we classified these factors as either hard or soft attributes of a hotel. We define hard attributes as matters regarding the hotel's physical or environmental aspects, such as facilities, location, or infrastructure. Some of these aspects would be impractical for the hotel to change, such as its surroundings and location. Others can be expensive to change, such as matters requiring construction costs, which are possible but regarding infrastructure investment. On the other hand, soft attributes are the non-physical attributes of the hotel service and staff behavior that are practical to change through management. For example, the hotel's services or the cleanliness of the rooms are soft attributes. For our purposes, amenities, clean or good quality bedsheets or curtains, and other physical attributes that are part of the service and not of the hotel's physical structure are also considered soft attributes. Thus, we can observe the top 10 satisfaction and dissatisfaction keywords and determine whether they are soft or hard attributes.

@@

    On the other hand, the word ``staff'' is the second or third in the lists of satisfaction factors in English-written reviews in all the price ranges. This word is followed by a few other keywords lower in the top 10 list, such as ``helpful'' or ``friendly''. When we look at the pairings of the top-ranked keyword ``good'' in Table \ref{tab:adj_en_pos}, we find that customers mostly praise the location, service, breakfast, or English availability. When we look at the negative keyword ``poor'' and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with. With these results, we can observe that both Chinese and English-speaking tourists in Japan have different priorities. However, both populations consider the hotel's location and transport availability (subways and trains) nearby as secondary but still essential points in their satisfaction with a hotel. The Chinese customers are primarily satisfied with the room quality in spaciousness and cleanliness and the service of breakfast.

@@

    We also can observe some keywords that are not considered by their counterparts. For example, English-speaking customers mentioned tobacco smell in many reviews. However, it was not statistically identified as a problem for their Chinese counterparts. On the other hand, while it appears in both English and Chinese lists, references to ``\begin{CJK}{UTF8}{gbsn}购物\end{CJK} (shopping)'' are more common in the Chinese lists across hotels of 15,000 yen to 200,000 yen per night. Meanwhile, the term ``shopping'' only appears in the 20,000 to 30,000 yen per night top 10 positive keywords list for English-speakers.

    In our research questions \ref{rsq:hard_soft} and \ref{rsq:hard_soft_diff}, we ponder how customers of both cultural backgrounds evaluate hard and soft attributes of the hotel and how they differ in those evaluations. Here we define hard attributes as those relating to the hotel's physical, structural, or environmental aspects. These are often impossible or impractical to change by the hotel management and staff, such as facilities, infrastructure, the surroundings, view, or location convenience. On the other hand, hotel staff and management can change soft attributes, for example, by improving the hotel's services via training or hiring specialized staff, improving the quantity or quality of amenities, bedsheets, or general cleanliness. Our study found that Chinese tourists are mostly positively reacting more to the hotel's hard attributes. There is a slightly hard leaning (53\%) concern with hard attributes in negative sentences, albeit this is more uniform than the positive evaluations. English-speaking tourists, on the other hand, are both positively and negatively more responsive to soft attributes. In the case of negative keywords, English-speaking tourists are overwhelmingly more concerned with the hotel's soft attributes dissatisfaction somehow.

    One factor that both populations have in common is, when perceiving the hotel negatively, ``\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)'', ``dated'', ``outdated'', or ``\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)'' aspects of the room or the hotel are being criticized across, surprisingly, most price ranges. This is, however, a hard attribute and is unlikely to change for most hotels.

@@

    We found that mainland Chinese tourists are satisfied mostly by Japanese hotels' big and clean spaces. From the adjectival pairings that we extracted with dependency parsing and POS tagging in Table \ref{tab:adj_zh_pos}, we can observe that mostly they mean big and clean rooms. Other mentions are also big markets nearby or a big bed. We can observe that across different price ranges, the usage of the word ``\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)'' increases as the hotel increases in price. However, we can see that they still react positively in a significant manner in cheaper hotels. Inspecting closer by taking random samples of the pairs of ``\begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space)'' or ``\begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area)'', we can see that there are also many references to the public bathing facilities in the hotel. We can also see them mentioned as a word pairing ``\begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring)''. In Japan, there is what is called ``\begin{CJK}{UTF8}{min}銭湯\end{CJK} (\textit{sent\=o})'', which are artificially made public bathing facilities, on occasions including saunas and baths with unique qualities. On the other hand, there are natural hot springs, called ``\begin{CJK}{UTF8}{gbsn}温泉\end{CJK} (\textit{onsen})''. They can either be bathing in the natural source of the water or using the hot springs in artificially made bath facilities. It is a Japanese custom and culture that all customers use the facilities after cleaning themselves in a shower and go into the baths without any clothes. It can be a cultural shock for many tourists, but this is a fundamental attraction for many.

@@

    One key component we found in Chinese customer satisfaction soft factors is the inclusion of breakfast within the hotel. While other food-related words were extracted, most of them were general, like ``food'' or ``eating,'' which were lower ranking. In contrast, the word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' refers possibly to its inclusion in the hotel commodities, was frequently used in positive texts compared to other food-related words. The word ``\begin{CJK}{UTF8}{gbsn}早餐\end{CJK} (breakfast)'' is also observed across all price ranges, although at different priorities in each of them. However, we assert that it is an important factor. Observing word pairs from the positive Chinese keywords in Table \ref{tab:adj_zh_pos}, we can also see that ``\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)'' is paired as ``\begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast)'' in four of the seven price ranges with reviews available as part of the top 4 pairings. It is only slightly lower on other categories, although it is not shown on the table. Thus we consider that a recommended strategy for hotel management is to invest in the inclusion or betterment of hotel breakfast to increase good reviews.

@@

    From the satisfaction factors of English-speaking tourists, we can see that at least three words relate directly to staff friendliness and services, being ``staff'', ``helpful'' and ``friendliness'' in the general database. The word ``staff'' is the second most frequently used word for satisfied customers across most price ranges, and only third in one of them. Adding to that, ``helpful'' and ``friendly'' follow it lower in the list in most price ranges. The word ``good'' is mostly about the location, the service, breakfast, or English availability in Table \ref{tab:adj_en_pos}. Like Chinese customers, Western customers also seem to enjoy the included breakfasts regarding their satisfaction keyword pairings. However, the word does not appear directly in the top 10 list as in their Chinese counterparts. The words ``helpful'' and ``friendly'' are mostly paired with ``staff'', ``concierge'', ``desk'', and ``service''. When we look at the negative keyword ‘poor’ and its pairings in Table \ref{tab:adj_en_neg}, we see that it is also service-related concepts that the Western tourists are disappointed with when they react negatively.

@@

    While less high in priority, the price range of 15,000 to 20,000 yen hotels also mentions ``free'' as one of the top 10 positive keywords, paired mostly with ``wifi''. This price range is mostly for business hotels, where we infer users would be expecting this feature the most. Western tourists are highly sensitive to comfort levels in the hotels and whether it reaches their expectations.

@@

  Below we explore the possible interactions with Japanese hospitality, the differences between Chinese and Western tourists, the possible cause for them, how they vary across different price ranges, and what they imply for the industry. We also discuss the differences between the hotel's hard and soft attributes and how they contribute to customers' satisfaction.
